Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-08 paper.tex
OpenStack

The first of them was {\tt MonteCarloMultiGPU} from NVIDIA SDK, launched with the default configuration ``scaling=weak'' which adjust the size of the problem depending on the number of accelerators.
The Figure~\ref{fig:mont-opt} depicts the options per second calculated by the application running on the scenarios of Figure~\ref{fig:aws} and on the instances with local GPUs. 
We have removed the results of the Scenario~\ref{subfig:aws2} for clarity ought to they are exactly the same that the obtained from Scenario~\ref{subfig:aws3} up to 8 GPUs. 
In other words, we could state that the results until the 8th GPU would correspond to the Scenario~\ref{subfig:aws2} and thereafter to the Scenario~\ref{subfig:aws3}.
Hence, in this particular case, rCUDA (using remote GPUs) is performing better than CUDA (with its local GPUs) due to rCUDA loads the libraries when its daemon starts.
However, even with rCUDA we can see differences in the results between booth scenarios. We determined that the Scenario~\ref{subfig:aws1} could increase the throughput because
unlike the other setups the GPUs are not sharing the PCI bus with other devices, as it happens in the 4-GPU instances.
% \begin{figure}[!t]
%   \centering
%   \includegraphics[width=\linewidth]{images/aws-mont2.png}
%   \caption{Montecarlo execution time}
%   \label{fig:mont-exe}
% \end{figure}
\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/mont.pdf}
  \caption{NVIDIA SDK {\tt MonteCarloMultiGPU} execution using local and remote GPUs.}
  \label{fig:mont-opt}
\end{figure}

The other application, LAMMPS\footnote{\url{http://lammps.sandia.gov}}, is a classical molecular dynamics simulator that can be applied at the atomic, meso, or continuum scale. 
From the implementation perspective, this multi-process application employs at least one GPU to host its processes, but can benefit from the use of multiple GPUs.
The Subfigure~\ref{subfig:lammps1} shows that running this application using remote GPUs does not offer any advantage in front of original CUDA. 
Furthermore, for the execution on remote GPUs, can be seen a little difference between both networks, the ``High'' network performs worse than ``10 Gb'' network.
Thus, if we compare the results of a LAMMPS execution with a larger problem (see Subfigure~\ref{subfig:lammps2}), although CUDA continues performing better, the interesting point is the execution time on remote GPUs. 
They are almost the same even with different networks what means that the transfers are making the interconnection network the bottleneck, and enlarging the problem size
pays off the drawback of a slower network.

@@

Version de open stack con la que se trabaja y tipo de instalacion ya que está toda en un nodo...

@@

\subsection{Experimental Results}
The tests were executed on a 5-node cluster where a machine
equipped with a Intel Xeon E7420 quadcore processor at
2.13 GHz, and 16 Gbytes of DDR2 RAM memory at 667
MHz, was guest host for the VMs. While the other 4 nodes
were auxiliary servers with a Tesla C1090 GPU each one. 
In the software stack the testbed system operates a
Centos 6.6; the cloud platform is deployed by OpenStack; and
the GPUs use CUDA 6.5. The GPU virtualization support is
based on rCUDA v5.0.

@@

MCUDA-MEME~\cite{Liu2010} has been the application executed with
different configurations in order to test the set-ups. MCUDA-
MEME is an MPI application which is accelerated by GPUs
Besides, each of its processes must have a GPU to not abort 
So, the number of GPUs will determine the number of processes that we can launch.

The Figure~\ref{fig3} shows and compares the execution time of
the application with different configurations over different setups. 
We have used up to 3 nodes to spread the processes and launched up to 8 processes (only 4 in exclusive mode), one for each remote GPU.
Firstly, we can state that the performance is higher with more than one node, because the traffic network is distributed among the nodes.
Secondly, the lowest execution time is obtained by both modes (exclusive and shared) when running their maximum number of processes with more than 1 node.
It could mean that it is not worthy to continue giving resources to the application to scale, because the performance growth rate is barely increasing.
Although, the time is lower sharing the GPUs the setup cannot take advantage of doubling the devices.

@@

\section{\uppercase{Discussion}}
\label{sec:discussion}
-Volver a hacer un resumen

@@

\section{\uppercase{Future work}}
\label{sec:future}
The first task that we should have keep in mind after this study is to upgrade the interconnection network to one more focused on HPC.
So that, porting the setup and the tests to an infrastructure with an Infiniband network would shed light on the viability of this kind of solutions for HPC.
The same thought, would guide us to try other Cloud vendors which more support for HPC.

Looking for real situations where the performance is not so important as the flexibility to provide more accelerators, 
would drive us to take the first steps through tools for easily deploying programming computer labs with the necessity for GPUs.

Finally, to bring in more strategies to decide where a remote GPUs is created and assigned to a physical device, would be an interesting task to carry out. 
With more scheduling policies the flexibility given by the GPGPU module for Openstack would increase.

>>>>

The first of them was {\tt MonteCarloMultigpu} from NVIDIA SDK, launched with the default configuration ``scaling=weak'' which adjust the size of the problem depending on the number of accelerators.
The Figure~\ref{fig:mont-opt} depicts the options per second calculated by the application running on the scenarios of Figure~\ref{fig:aws} and on the instances with local GPUs. 
We have removed the results of the Scenario~\ref{subfig:aws2} for clarity ought to they are exactly the same that the obtained from Scenario~\ref{subfig:aws3} up to 8 GPUs. 
In other words, we could state that the results until the 8th GPU would correspond to the Scenario~\ref{subfig:aws2} and thereafter to the Scenario~\ref{subfig:aws3}.
Hence, in this particular case, rCUDA (using remote GPUs) is performing better than CUDA (with its local GPUs) due to rCUDA loads the libraries when its daemon starts.
However, even with rCUDA we can see differences in the results between booth scenarios. We determined that the Scenario~\ref{subfig:aws1} could increase the throughput because
unlike the other setups the GPUs are not sharing the PCI bus with other devices, as it happens in the 4-GPU instances.
% \begin{figure}[!t]
%   \centering
%   \includegraphics[width=\linewidth]{images/aws-mont2.png}
%   \caption{Montecarlo execution time}
%   \label{fig:mont-exe}
% \end{figure}
\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{images/mont.pdf}
  \caption{NVIDIA SDK {\tt MonteCarloMultiGPU} execution using local and remote GPUs.}
  \label{fig:mont-opt}
\end{figure}

The other application, LAMMPS\footnote{\url{http://lammps.sandia.gov}}, is a classical molecular dynamics simulator that can be applied at the atomic, meso, or continuum scale. 
From the implementation perspective, this multi-process application employs at least one GPU to host its processes, but can benefit from the use of multiple GPUs.
The Figure shows that running this application using remote GPUs does not offer any advantage in front of original CUDA. 
Furthermore, for the execution on remote GPUs, can be seen a little difference between both networks, the ``High'' network performs worse than ``10 Gb'' network.
Thus, if we compare the results of a LAMMPS execution with a larger problem (see Figure), although CUDA continues performing better, the interesting point is the execution time on remote GPUs. 
They are almost the same even with different networks what means that the transfers are making the interconnection network the bottleneck, and enlarging the problem size
pays off the drawback of a slower network.

@@

@@

\subsection{Experimental Results}
The test were executed on a 5-node cluster where a machine
equipped with a Intel Xeon E7420 quadcore processor at
2.13 GHz, and 16 Gbytes of DDR2 RAM memory at 667
MHz, was guest host for the VMs. While the other 4 nodes
were auxiliary servers with a Tesla C1090 GPU each one. 
In the software stack the testbed system operates a
Centos 6.6; and the GPUs use CUDA 6.5. The GPU virtualization support is
based on rCUDA v5.0. In order to deploy an infrastructure as a service cloud,
we installed OpenStack Icehouse version and QEMU/KVM 0.12.1 as the hypervisor in one
of these 5-node cluster. A fully-featured OpenStack deployment usually requires
at least three nodes: one controller node that manages the compute nodes 
where the VMs are hosted, one network node that manages the logic
virtual network for the VMs, and one or more compute nodes that 
run the hypervisor and virtual machines. However, our OpenStack deployment
was deployed in one-node architecture making better use of our resources.
Thus, the main OpenStack services such as identity, image, compute, dashboard, and 
network services were installed in the first machine without GPU described above.

@@

MCUDA-MEME~\cite{Liu2010} has been the application executed with
different configurations in order to test the set-ups. MCUDA-
MEME is GPGPU MPI application, so the number of GPUs
will determine the number of executable processes.
The Figure~\ref{fig3} shows and compares the execution time of
the application with different configurations over different set-
ups. We can determine that with 1 node, the performance is
lower, with 2 and 3 is quite similar, though. Hence, the greatest
difference can be appreciated between modes, where the
highest performance is achieved by sharing the accelerators.

@@

\section{\uppercase{Discussion}}
\label{sec:discussion}
-Volver a hacer un resumen
-posibles futuras aplicaciones (lab)
-pruebas con otros proveedores o con otras plataformas (azure)

@@

\section{\uppercase{Future work}}
\label{sec:future}
The first task that we should have keep in mind after this study is to upgrade the interconnection network to one more focused on HPC.
So that, porting the setup and the tests to an infrastructure with an Infiniband network would shed light on the viability of this kind of solutions for HPC.

Looking for real situations where the performance is not so important as the flexibility to provide more accelerators, 
would drive us to take the first steps through tools for easily deploying programming computer labs with the necessity for GPU.

Finally, to bring in more strategies to decide where a remote GPUs was created and assigned to a physical device, would be an interesting task to carry out. 
With more scheduling policies the flexibility given by the GPGPU module for Openstack should increase.
